### 2024-11-10 README.Rmd
magnitude(), normalize(), and arbitrary modeling functions for embed_docs()

valence_df <- valence_df |> 
	embed_docs("text", glove_twitter_25d, id_col = "id", .keep_all = TRUE)
valence_df
```

To quantify how good and how intense these texts are, we can compare them to the embeddings for "good" and "intense" using `get_similarities()`. Note that this step requires only a dataframe or tibble with numeric columns; the embeddings can come from any source.

```{r}
good_vec <- predict(glove_twitter_25d, "good")
intense_vec <- predict(glove_twitter_25d, "intense")
valence_quantified <- valence_df |> 
	get_similarities(
		dim_1:dim_25, 
		list(
			good = good_vec, 
			intense = intense_vec
			)
		)
valence_quantified
```
### Example Quanteda Workflow

@@

```{r}
valence_df_2d <- valence_df |> 
	reduce_dimensionality(dim_1:dim_25, 2)
valence_df_2d
```
#### Normalize or Center

@@

>>>>

valence_embeddings_df <- valence_df |> 
	embed_docs("text", glove_twitter_25d, id_col = "id", .keep_all = TRUE)
valence_embeddings_df
```

`embed_docs()` can also be used to generate other types of embeddings. For example, we can use the '[text](https://r-text.org)' package to generate embeddings using any model available from Huggingface transformers.

```{r, eval=FALSE}
sbert_embeddings <- function(texts) {
	text::textEmbed(
	  texts,
	  model = "sentence-transformers/all-MiniLM-L12-v2", # model name
	  layers = -2,  # second to last layer (default)
	  tokens_select = "[CLS]", # use only [CLS] token
	  dim_name = FALSE,
	  keep_token_embeddings = FALSE
  )$texts[[1]]
}

valence_sbert_df <- valence_df |> 
	embed_docs("text", sbert_embeddings, id_col = "id", .keep_all = TRUE)
```

To quantify how good and how intense the texts are, we can compare them to the embeddings for "good" and "intense" using `get_similarities()`. Note that this step requires only a dataframe,  tibble, or embeddings object with numeric columns; the embeddings can come from any source.

```{r}
good_vec <- predict(glove_twitter_25d, "good")
intense_vec <- predict(glove_twitter_25d, "intense")
valence_quantified <- valence_embeddings_df |> 
	get_similarities(
		dim_1:dim_25, 
		list(
			good = good_vec, 
			intense = intense_vec
			)
		)
valence_quantified
```
### Example Quanteda Workflow

```{r}
library(quanteda)

valence_corp <- corpus(valence_df, docid_field = "id")
valence_corp

valence_dfm <- valence_corp |> 
	tokens() |> 
	dfm()

valence_embeddings_df <- valence_dfm |> 
	textstat_embedding(glove_twitter_25d)
valence_embeddings_df
```

@@

```{r}
valence_df_2d <- valence_embeddings_df |> 
	reduce_dimensionality(dim_1:dim_25, 2)
valence_df_2d
```
#### Normalize (Scale Embeddings to the Unit Hypersphere)

```{r}
normalize(good_vec)

normalize(moral_embeddings)

valence_embeddings_df |> normalize_rows(dim_1:dim_25)
```

@@

```{r}
magnitude(good_vec)

magnitude(moral_embeddings)
```
